Sequence assembly

### 2023-05-16 episodes/sequence-assembly.Rmd
Added snp phylogeny, removed code of conduct and contributing, adapted license

```bash
$ for sample in ERR029206 ERR029207
>  do
>  skesa \
--cores 2 \
--memory 8 \
--fastq "${sample}"_1.fastq.gz_trim.fastq "${sample}"_2.fastq.gz_trim.fastq 1> ~/molepi/results/assembly/"${sample}".fasta
>  done
```

@@

```
$ assembly-stats
```

prints information about an assembly.

@@

```bash
assembly-stats ERR026473.fasta
wc -l infoalign err026743.fasta
...
ERR026473.fasta:390
ERR026474.fasta:367
ERR026478.fasta:296
ERR026481.fasta:336
ERR026482.fasta:345
ERR029206.fasta:451
ERR029207.fasta:458
```

>>>>

```bash
$ for sample in ERR029206 ERR029207
do
skesa \
--cores 2 \
--memory 8 \
--fastq "${sample}"_1.fastq.gz_trim.fastq "${sample}"_2.fastq.gz_trim.fastq 1> ../../results/assembly/"${sample}".fasta
done
```

@@

@@

```bash
assembly-stats ERR026473.fasta
```

```output
stats for ERR029206.fasta
sum = 4233864, n = 451, ave = 9387.73, largest = 70968
N50 = 20633, n = 68
N60 = 16723, n = 91
N70 = 13473, n = 120
N80 = 9592, n = 157
N90 = 5883, n = 213
N100 = 200, n = 451
N_count = 0
Gaps = 0
```
